---
title: "Coordinate Systems"
author: "Ben Pearce"
date: "2026-07-29"
output: pdf_document
---



1. NZGD2000 (Most common)

This is the official geodetic datum for New Zealand and is used by:

LINZ
GeoNet
Stats NZ
Most government GIS datasets

It defines the latitude and longitude system for New Zealand.

Geographic coordinates
Datum: NZGD2000
CRS: EPSG:4167


2. NZTM2000 (Most common projected CRS)

New Zealand Transverse Mercator 2000 (NZTM2000) is the standard projected coordinate system.

EPSG: 2193

Instead of latitude/longitude, coordinates are measured in metres.


3. WGS84 (GPS)
EPSG: 4326

This is the global coordinate system used by:

GPS
Google Maps
OpenStreetMap
Most web maps

4. Historical coordinate systems

Older datasets may use:

CRS	EPSG	Status
NZGD1949	4272	Old datum
NZMG (NZ Map Grid)	27200	Obsolete but still seen in older datasets

If you're working with historical maps or older government data, you may need to convert these to NZGD2000 or NZTM2000.




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
library(sF)
```


# Check the Coordinate Reference System
```{r}

data <- st_read("your_file.shp")

st_crs(data)

```

