---
title: "R Notebook"
output: html_notebook
---


Picked >= 5 felt reports because it looked good, Hazel has said we need to have strong justification.
She suggested comparing the standard deviation as the minimum number of felt reports are needed, and standard error for random effects.




# Data Preparation
Reads the two datasets and joins the Vs30 data to the main dataset based on the nearest Vs30 data point.

```{r}
library(arrow)
library(MASS)
library(tidyverse)
library(sf)
library(leaps)
library(lme4)


data <- read_parquet("data.parquet")

data_sf <- data |>
  st_as_sf(
    coords = c("longitude", "latitude"),
    crs = 4326,
    remove = FALSE
  )


# filters the dataset to the decided upon report count
data_sf <- data_sf |>
  filter(report_count >= 4)
```
# Box-Cox Transformation

Uses a Box-Cox transformation to find the most suitable transformation of `reported_mmi` for the full dataset.

```{r}
bc <- boxcox(
  lm(reported_mmi ~ felt_median, data = data_sf)
)

best_lambda <- bc$x[which.max(bc$y)]

best_lambda
```


# Box-Cox Model

Applies the selected Box-Cox transformation using lambda = -1.3 and fits a linear model using `felt_median` as the predictor.

```{r}
data_sf <- data_sf |>
  mutate(
    mmi_bc_1.3 = (reported_mmi^(-1.3) - 1) / (-1.3)
  )

model_bc <- lm(mmi_bc_1.3 ~ felt_median, data = data_sf)

plot(model_bc)
summary(model_bc)
```
# Best Subset Selection — Full Dataset

Uses best subset selection to compare combinations of earthquake depth, hypocentral distance, felt median, moment magnitude and Vs30 for predicting the Box-Cox transformed MMI.


```{r}
model_lr_rss <- regsubsets(
  reported_mmi ~ event_depth_km + Rhypo_km + felt_median + Vs30_raw + mt_Mw,
  data = data_sf,
  nvmax = 5
)

summary(model_lr_rss)
plot(model_lr_rss)
summary(model_lr_rss)$bic
```

# Filtering Felt Reports

With the selected variables applies a Box-Cox analysis to determine the most suitable transformation for the filtered data.

```{r}
model_lr_bc <- boxcox(
  lm(reported_mmi ~ event_depth_km + Rhypo_km + felt_median + Vs30_raw + mt_Mw, data = data_sf)
)

best_lambda <- model_lr_bc$x[which.max(model_lr_bc$y)]
best_lambda
```



# Selected Linear Model — Full Dataset

Fits the model selected from the best subset analysis and boxcox transformations and checks its model summary and diagnostic plots.
Note: A value of -1 was used instead of -1.272727 for simplicity, as both transformations produced very similar diagnostic plots and model results.

```{r}
data_sf <- data_sf |>
  mutate(
    mmi_bc_neg1 = (reported_mmi^(-1) - 1) / (-1)
  )

model_lr <- lm(
  mmi_bc_neg1 ~ event_depth_km + Rhypo_km + felt_median + Vs30_raw + mt_Mw, data = data_sf
  )

plot(model_lr)
summary(model_lr)
```


# Mixed-Effects Model

Fits a linear mixed-effects model with earthquake ID (`publicid`) as a random effect to account for multiple observations coming from the same earthquake.
still very Work in progress

```{r}

model_mem_1 <- lmer(
  log(reported_mmi) ~ Rhypo_km + event_depth_km + Vs30_raw +
    (1 | publicid),
  data = data_sf
)

summary(model_mem)
```