---
title: "R Notebook"
output: html_notebook
---


Picked >= 5 felt reports because it looked good, Hazel has said we need to have strong justification.
She suggested comparing the standard deviation as the minimum number of felt reports are needed, and standard error for random effects.




# Data Preparation
Reads the two datasets and joins the Vs30 data to the main dataset based on the nearest Vs30 data point.

```{r}
library(arrow)
library(MASS)
library(tidyverse)
library(sf)
library(leaps)
library(lme4)


data <- read_parquet("data.parquet")

data_sf <- data |>
  st_as_sf(
    coords = c("longitude", "latitude"),
    crs = 4326,
    remove = FALSE
  )

vs30_data <- read_parquet("data_processed/vs30_site_lookup.parquet")

vs30_sf <- vs30_data |>
  st_as_sf(
    coords = c("report_longitude", "report_latitude"),
    crs = 4326,
    remove = FALSE
  ) |>
  filter(!is.na(Vs30_raw))

nearest_id <- st_nearest_feature(data_sf, vs30_sf)

data_sf <- data_sf |>
  mutate(
    Vs30_raw = vs30_sf$Vs30_raw[nearest_id]
  )
```
# Box-Cox Transformation

Uses a Box-Cox transformation to find the most suitable transformation of `reported_mmi` for the full dataset.

```{r}
bc <- boxcox(
  lm(reported_mmi ~ felt_median, data = data_sf)
)

best_lambda <- bc$x[which.max(bc$y)]

best_lambda
```
# Box-Cox Model

Applies the selected Box-Cox transformation using lambda = -1.3 and fits a linear model using `felt_median` as the predictor.

```{r}
data_sf <- data_sf |>
  mutate(
    mmi_bc_1.3 = (reported_mmi^(-1.3) - 1) / (-1.3)
  )

model_bc <- lm(mmi_bc_1.3 ~ felt_median, data = data_sf)

plot(model_bc)
summary(model_bc)
```
# Filtering Felt Reports

Filters the dataset to observations with at least five reports and repeats the Box-Cox analysis to determine the most suitable transformation for the filtered data.

```{r}
data_sf_5 <- data_sf |>
  filter(report_count >= 5)


bc <- boxcox(
  lm(reported_mmi ~ felt_median, data = data_sf_5)
)

best_lambda <- bc$x[which.max(bc$y)]

best_lambda

```
# Log-Transformed Model

Fits a linear model using the log transformation suggested by the Box-Cox analysis for observations with at least five reports.

```{r}

model_bc_5 <- lm(log(reported_mmi) ~ felt_median, data = data_sf_5)

plot(model_bc_5)
summary(model_bc_5)
```
# Best Subset Selection — Full Dataset

Uses best subset selection to compare combinations of earthquake depth, hypocentral distance, felt median, and Vs30 for predicting the Box-Cox transformed MMI.


```{r}
best <- regsubsets(
  mmi_bc_1.3 ~ event_depth_km + Rhypo_km + felt_median + Vs30_raw,
  data = data_sf,
  nvmax = 4
)

summary(best)

plot(best)

summary(best)$bic
```
# Selected Linear Model — Full Dataset

Fits the model selected from the best subset analysis and checks its model summary and diagnostic plots.

```{r}
best_lm_1.3 <- lm(mmi_bc_1.3 ~ event_depth_km + Rhypo_km + felt_median,
  data = data_sf
)

summary(best_lm_1.3)
plot(best_lm_1.3)
```

# Best Subset Selection — Filtered Dataset

Uses best subset selection on observations with at least five reports to find the best combination of predictors for log-transformed MMI.

```{r}
best <- regsubsets(
  log(reported_mmi) ~ event_depth_km + Rhypo_km + felt_median + Vs30_raw,
  data = data_sf_5,
  nvmax = 4
)

summary(best)

plot(best)

summary(best)$bic
```
# Selected Linear Model — Filtered Dataset

Fits the selected linear model for the filtered dataset and checks its summary and diagnostic plots.

```{r}
best_lm <- lm(log(reported_mmi) ~ event_depth_km + Rhypo_km + felt_median + Vs30_raw,
  data = data_sf_5
)

summary(best_lm)
plot(best_lm)
```

# Mixed-Effects Model

Fits a linear mixed-effects model with earthquake ID (`publicid`) as a random effect to account for multiple observations coming from the same earthquake.
still very Work in progress

```{r}

model_mem <- lmer(
  log(reported_mmi) ~ Rhypo_km + event_depth_km + Vs30_raw +
    (1 | publicid),
  data = data_sf
)

summary(model_mem)
```