---
title: "tree"
format: typst
editor: visual
---

## Turn data into classification prob, MMI point is treated as oridinal.

```{r}
library(tree)
library(dplyr)
library(rpart)
library(randomForest)
library(gbm)
library(arrow)
library(pROC)
```

Read Yanxi file

```{r}
earthquake_data = read_parquet('data_processed/NZ_FR_IAR_modelling_strict_mtMw.parquet')
```

```{r}
glimpse(earthquake_data)

earthquake_data_trim <- earthquake_data[, c("publicid",
                                       "Mw_model",
                                       "Mw",
                                       "M_model_is_Mw",
                                       "Mw_strict",
                                       "Repi_km",
                                       "Rhypo_km",
                                       "Rcentroid_km",
                                       "Vs30_m_s",
                                       "ln_Vs30",
                                       "reported_mmi",
                                       "report_count",
                                       "fault_style",
                                       "has_felt_rapid",
                                       "has_moment_tensor"
                                        
)]

glimpse(earthquake_data_trim)
```

```{r}
colnames(earthquake_data_trim)

table(earthquake_data_trim$reported_mmi)

unique(earthquake_data_trim$fault_style)
```

MMI value below 3 is only 7 observations recorded. The fact that below 3 MMI is very hard for human to really consider correctly report, therefore removing observation below 3, giving 197421 - 7 = 197414 total MMI count.

```{r}
colSums(is.na(earthquake_data_trim))

earthquake_data_trim <- earthquake_data_trim[earthquake_data_trim$reported_mmi >= 3, ]

table(earthquake_data_trim$reported_mmi)
```

Changing MMI to ordinal data

```{r}
earthquake_data_trim$reported_mmi <- ordered(earthquake_data_trim$reported_mmi, levels = 3:8)
```

```{r}
summary(earthquake_data_trim)

all(earthquake_data_trim$Mw_model == earthquake_data_trim$Mw,
    earthquake_data_trim$Mw_model == earthquake_data_trim$Mw_strict
)
```

After summary their are quite some columns that actually the same: Mw_model, Mw, Mw_strict, remove and only keep one. Sanity check columns as has_moment_tensor and has_felt_rapid also being removed. Column fault_style is also changed into nominal data and NA change into "unknown" for tree model.

```{r}
earthquake_data_trim <- earthquake_data_trim[, c("publicid",
                                                 "Mw",
                                            "Repi_km",
                                            "Rhypo_km",
                                            "Rcentroid_km",
                                            "Vs30_m_s",
                                            "ln_Vs30",
                                            "reported_mmi",
                                            "report_count",
                                            "fault_style"
)]


earthquake_data_trim$fault_style[is.na(earthquake_data_trim$fault_style)] <- "unknown"

earthquake_data_trim$fault_style <- factor(earthquake_data_trim$fault_style)
```

```{r}
glimpse(earthquake_data_trim)
```

```{r}
hist(
  earthquake_data_trim$Vs30_m_s,
  breaks = 50,
  main = "Distribution of Vs30",
  xlab = "Vs30 (m/s)",
  ylab = "Frequency"
)
```

```{r}
hist(
  earthquake_data_trim$ln_Vs30,
  breaks = 50,
  main = "Distribution of ln(Vs30)",
  xlab = "ln(Vs30)",
  ylab = "Frequency"
)
```

Even with slightly skew data of Vs30, it is still meaningful for tree model, therefore no need to smooth data with ln_Vs30, removing the column.

```{r}
earthquake_data_trim <- earthquake_data_trim[, c("publicid",
                                                 "Mw",
                                                 "Repi_km",
                                                 "Rhypo_km",
                                                 "Rcentroid_km",
                                                 "Vs30_m_s",
                                                 "reported_mmi",
                                                 "report_count",
                                                 "fault_style"
)]
```

Split data for train and test

```{r}
set.seed(1911)

publicids <- unique(earthquake_data_trim$publicid)

train_ids <- sample(publicids, size = floor(0.8 * length(publicids)))

train <- earthquake_data_trim[earthquake_data_trim$publicid %in% train_ids,]

test <- earthquake_data_trim[!earthquake_data_trim$publicid %in% train_ids,]


dim(train)
dim(test)
```

```{r}
tree_earthquake <- tree(reported_mmi ~., train)

summary(tree_earthquake)
```

```{r}
plot(tree_earthquake)
text(tree_earthquake, pretty = 0, cex = 0.8)
tree_earthquake
```

```{r}
cv_tree_earthquake <- cv.tree(tree_earthquake, FUN = prune.misclass, K = 10)

plot(cv_tree_earthquake$size, cv_tree_earthquake$dev, type = 'b')
```

Cross validation shows 2 to 4 node is acceptable. Prune and check.

```{r}
prune_eq_2 <- prune.misclass(tree_earthquake, best = 2)

plot(prune_eq_2)
text(prune_eq_2, pretty = 0, cex = 0.8)
```

```{r}
prune_eq_3 <- prune.misclass(tree_earthquake, best = 3)

plot(prune_eq_3)
text(prune_eq_3, pretty = 0, cex = 0.8)
```

```{r}
prune_eq_4 <- prune.misclass(tree_earthquake, best = 4)

plot(prune_eq_4)
text(prune_eq_4, pretty = 0, cex = 0.8)
```

Checking trees with cinfusing matrix

```{r}
prune_2_pred <- predict(prune_eq_2, test, type = 'class')

table(prune_2_pred, test$reported_mmi)
```

```{r}
prune_3_pred <- predict(prune_eq_3, test, type = 'class')

table(prune_3_pred, test$reported_mmi)
```

```{r}
prune_4_pred <- predict(prune_eq_4, test, type = 'class')

table(prune_4_pred, test$reported_mmi)
```

Three prune tree share the same confusing matrix. Accuracy is calculated

```{r}
accuracy1 <- sum(diag(table(prune_3_pred, test$reported_mmi))) / sum(table(prune_3_pred, test$reported_mmi))

accuracy1
```

```{r}
diag(table(prune_3_pred, test$reported_mmi)) / colSums(table(prune_3_pred, test$reported_mmi))
```

Not very high, as high as wild guess

Build tree using library Rpart

```{r}
set.seed(1911)

tree_rpart <- rpart(reported_mmi ~ Mw + Repi_km + Rhypo_km +Rcentroid_km + Vs30_m_s + fault_style, data = train, method = "class", control = rpart.control(cp = 0, minsplit = 2)
)

tree_rpart$cptable
plotcp(tree_rpart)
plot(tree_rpart)
text(tree_rpart, pretty = 0, cex = 0.8)
```

```{r}
min(tree_rpart$cptable[, "xerror"])

min_cv <- which.min(tree_rpart$cptable[, "xerror"]) 
prune_rpart <- prune(tree_rpart, cp = tree_rpart$cptable[min_cv, "CP"])
```

```{r}
plot(prune_rpart, main = "prune tree")
text(prune_rpart, cex = 0.6)
```

```{r}
pred_rpart <- predict(prune_rpart, test, type = "class")

rpart_matrix <- table( Predicted = pred_rpart,Actual = test$reported_mmi)


```

```{r}
accuracy2 <- sum(diag(rpart_matrix)) / sum(rpart_matrix)
accuracy2
```

```{r}
diag(rpart_matrix) / colSums(rpart_matrix)
```

Recall seems better but MMI 6 to 8 is unregconizable.

Bagging

```{r}
set.seed(1911)

bagging <- randomForest(reported_mmi ~ Mw + Repi_km + Rhypo_km + Rcentroid_km + Vs30_m_s + fault_style, data = train, mtry = 6, ntree = 1000, importance = TRUE, do.trace = 100)

bagging
```

```{r}
bag_pred <- predict(bagging, test)

bag_matrix <- table(Predicted = bag_pred, Actual = test$reported_mmi)

bag_matrix
```

```{r}
accuracy3 <- sum(diag(bag_matrix)) / sum(bag_matrix)

accuracy3
```

```{r}
diag(bag_matrix) / colSums(bag_matrix)

```

```{r}
importance(bagging, type = 2)
varImpPlot(bagging, type = 2)
```

Random forest

```{r}
set.seed(1911)

rf <- randomForest(reported_mmi ~ Mw + Repi_km + Rhypo_km + Rcentroid_km + Vs30_m_s + fault_style, data = train, ntree = 1000, importance = TRUE, do.trace = 100)

rf
```

```{r}
importance(rf, type = 2)
varImpPlot(rf, type = 2, main = "Variable Importance - Random Forest")
```

```{r}
rf_pred <- predict(rf, test)

rf_matrix <- table(Predicted = rf_pred, Actual = test$reported_mmi)

rf_matrix
```

```{r}
accuracy4 <- sum(diag(rf_matrix)) / sum(rf_matrix)

accuracy4
```

```{r}
diag(rf_matrix) / colSums(rf_matrix)
```

Bagging and random forest have a bit higher accuracy and recall of MMi but still not desirable.

Boosting

```{r}
set.seed(1911)

boost <- gbm(reported_mmi ~ Mw + Repi_km + Rhypo_km + Rcentroid_km + Vs30_m_s + fault_style, 
             data = train, 
             distribution = "multinomial", 
             n.trees = 1000, 
             interaction.depth = 4, 
             shrinkage = 0.01, 
             n.minobsinnode = 10,
             cv.folds = 5,
             verbose = FALSE)

summary(boost)
```

Boost tree is different from decision tree, random forest, it pays more attention to Mw and distance variable than Vs30.

```{r}
optimize_boost <- gbm.perf(boost, method = "OOB")
optimize_boost
```

```{r}
boost_prob <- predict(boost, test, n.trees = optimize_boost, type = "response")
boost_prob <- drop(boost_prob)

boost_pred <- colnames(boost_prob)[max.col(boost_prob)]

boost_pred <- factor(boost_pred,levels = levels(test$reported_mmi))

boost_matrix <- table(Predicted = boost_pred, Actual = test$reported_mmi)

boost_matrix
```

```{r}
accuracy5 <- sum(diag(boost_matrix)) / sum(boost_matrix)

accuracy5
```

```{r}
diag(boost_matrix) / colSums(boost_matrix)
```

ROC and AUC to compare models

```{r}
prune3_prob <- predict(prune_eq_3, test, type = "vector")
rpart_prob  <- predict(prune_rpart, test, type = "prob")
bag_prob    <- predict(bagging, test, type = "prob")
rf_prob     <- predict(rf, test, type = "prob")
# boost_prob đã có sẵn từ phần Boosting ở trên (đã drop chiều thừa)
```

AUC multiclass, Hand & Till

```{r}
roc_prune3 <- multiclass.roc(test$reported_mmi, prune3_prob)
roc_rpart  <- multiclass.roc(test$reported_mmi, rpart_prob)
roc_bag    <- multiclass.roc(test$reported_mmi, bag_prob)
roc_rf     <- multiclass.roc(test$reported_mmi, rf_prob)
roc_boost  <- multiclass.roc(test$reported_mmi, boost_prob)

auc_table <- data.frame(Model = c("Pruned tree (best = 3)", "Rpart", "Bagging", "Random Forest", "Boosting"), AUC = c(auc(roc_prune3), auc(roc_rpart), auc(roc_bag), auc(roc_rf), auc(roc_boost))
)

auc_table[order(-auc_table$AUC), ]
```

ROC of one MMI level comparing the rest level to see if it is distinguishable by each model

```{r}
mmi_levels <- levels(test$reported_mmi)

plot_ovr_roc <- function(prob_matrix, actual, model_name) {
  colors <- rainbow(length(mmi_levels))
  plot(0, 0, type = "n", xlim = c(0, 1), ylim = c(0, 1),
       xlab = "False Positive Rate", ylab = "True Positive Rate",
       main = paste("One-vs-Rest ROC -", model_name))
  abline(a = 0, b = 1, lty = 2, col = "gray")

  aucs <- numeric(length(mmi_levels))
  for (i in seq_along(mmi_levels)) {
    lvl <- mmi_levels[i]
    binary_actual <- as.numeric(actual == lvl)
    roc_obj <- roc(binary_actual, prob_matrix[, lvl], quiet = TRUE)
    lines(1 - roc_obj$specificities, roc_obj$sensitivities, col = colors[i], lwd = 2)
    aucs[i] <- auc(roc_obj)
  }

  legend("bottomright",
         legend = paste0("MMI ", mmi_levels, " (AUC = ", round(aucs, 2), ")"),
         col = colors, lwd = 2, cex = 0.6)

  invisible(setNames(aucs, mmi_levels))
}
```

```{r}
plot_ovr_roc(prune3_prob, test$reported_mmi, "Pruned tree (best = 3)")
```

```{r}
plot_ovr_roc(rpart_prob, test$reported_mmi, "Rpart")
```

```{r}
plot_ovr_roc(bag_prob, test$reported_mmi, "Bagging")
```

```{r}
plot_ovr_roc(rf_prob, test$reported_mmi, "Random Forest")
```

```{r}
plot_ovr_roc(boost_prob, test$reported_mmi, "Boosting")
```
