---
title: "tree"
format: typst
editor: visual
---

## Turn data into classification prob, MMI point is treated as oridinal.

```{r}
library(tree)
library(dplyr)
library(rpart)
library(randomForest)
library(gbm)
library(arrow)
library(pROC)
library(caret)
```

Read Yanxi file

```{r}
earthquake_data = read_parquet('data_processed/NZ_FR_IAR_modelling_strict_mtMw.parquet')
```

```{r}
#glimpse(earthquake_data)

earthquake_data_trim <- earthquake_data[, c("publicid",
                                       "Mw_model",
                                       "Mw",
                                       "M_model_is_Mw",
                                       "Mw_strict",
                                       "Repi_km",
                                       "Rhypo_km",
                                       "Rcentroid_km",
                                       "Vs30_m_s",
                                       "ln_Vs30",
                                       "reported_mmi",
                                       "report_count",
                                       "fault_style",
                                       "has_felt_rapid",
                                       "has_moment_tensor"
                                        
)]

#glimpse(earthquake_data_trim)
```

```{r}
colnames(earthquake_data_trim)

table(earthquake_data_trim$reported_mmi)

unique(earthquake_data_trim$fault_style)
```

MMI value below 3 is only 7 observations recorded. The fact that below 3 MMI is very hard for human to really consider correctly report, therefore removing observation below 3, giving 197421 - 7 = 197414 total MMI count.

```{r}
#colSums(is.na(earthquake_data_trim))

earthquake_data_trim <- earthquake_data_trim[earthquake_data_trim$reported_mmi >= 3, ]

#table(earthquake_data_trim$reported_mmi)
```

Changing MMI to ordinal data

```{r}
earthquake_data_trim$reported_mmi <- ordered(earthquake_data_trim$reported_mmi, levels = 3:8)
```

```{r}
summary(earthquake_data_trim)

all(earthquake_data_trim$Mw_model == earthquake_data_trim$Mw,
    earthquake_data_trim$Mw_model == earthquake_data_trim$Mw_strict
)
```

After summary their are quite some columns that actually the same: Mw_model, Mw, Mw_strict, remove and only keep one. Sanity check columns as has_moment_tensor and has_felt_rapid also being removed. Column fault_style is also changed into nominal data and NA change into "unknown" for tree model.

```{r}
earthquake_data_trim <- earthquake_data_trim[, c("publicid",
                                                 "Mw",
                                            "Repi_km",
                                            "Rhypo_km",
                                            "Rcentroid_km",
                                            "Vs30_m_s",
                                            "ln_Vs30",
                                            "reported_mmi",
                                            "report_count",
                                            "fault_style"
)]


earthquake_data_trim$fault_style[is.na(earthquake_data_trim$fault_style)] <- "unknown"

earthquake_data_trim$fault_style <- factor(earthquake_data_trim$fault_style)
```



```{r}
hist(
  earthquake_data_trim$Vs30_m_s,
  breaks = 50,
  main = "Distribution of Vs30",
  xlab = "Vs30 (m/s)",
  ylab = "Frequency"
)
```

```{r}
hist(
  earthquake_data_trim$ln_Vs30,
  breaks = 50,
  main = "Distribution of ln(Vs30)",
  xlab = "ln(Vs30)",
  ylab = "Frequency"
)
```

Slightly skew data of Vs30 and centralized, however to get value not too separate retain ln_Vs30, therefore removethe column Vs30.

```{r}
earthquake_data_trim <- earthquake_data_trim[, c("publicid",
                                                 "Mw",
                                                 "Repi_km",
                                                 "Rhypo_km",
                                                 "Rcentroid_km",
                                                 "ln_Vs30",
                                                 "reported_mmi",
                                                 "fault_style"
)]
```

Split data for train and test

```{r}
set.seed(1911)

publicids <- unique(earthquake_data_trim$publicid)

train_ids <- sample(publicids, size = floor(0.8 * length(publicids)))

train <- earthquake_data_trim[earthquake_data_trim$publicid %in% train_ids,]

test <- earthquake_data_trim[!earthquake_data_trim$publicid %in% train_ids,]


#dim(train)
#dim(test)
```

## Function for models evaluation

```{r}
mmi_levels <- levels(train$reported_mmi)
n_class    <- length(mmi_levels)

# confusion matrix, accuracy, balanced accuracy, recall, AUC multiclass
eval_summary <- function(pred_class, prob_matrix, actual, model_name) {
  cm <- table(Predicted = pred_class, Actual = actual)
  acc <- sum(diag(cm)) / sum(cm)
  recall <- diag(cm) / colSums(cm)
  precision <- diag(cm) / rowSums(cm)
  bal_acc <- mean(recall, na.rm = TRUE)

  cat("----", model_name, "----\n")
  print(cm)
  cat("\nAccuracy:", round(acc, 4), "\n")
  cat("Balanced accuracy (mean recall):", round(bal_acc, 4), "\n")
  cat("Precision theo từng mức MMI:\n")
  print(round(precision, 3))
  cat("Recall theo từng mức MMI:\n")
  print(round(recall, 3))

  roc_multi <- multiclass.roc(actual, prob_matrix)
  auc_val <- as.numeric(auc(roc_multi))
  cat("\nMulticlass AUC (Hand & Till):", round(auc_val, 4), "\n")

  invisible(list(cm = cm, accuracy = acc, balanced_accuracy = bal_acc,
                 recall = recall, auc = auc_val))
}

# ROC one-vs-rest 
plot_ovr_roc <- function(prob_matrix, actual, model_name) {
  colors <- rainbow(length(mmi_levels))
  plot(0, 0, type = "n", xlim = c(0, 1), ylim = c(0, 1),
       xlab = "False Positive Rate", ylab = "True Positive Rate",
       main = paste("One-vs-Rest ROC -", model_name))
  abline(a = 0, b = 1, lty = 2, col = "gray")

  aucs <- numeric(length(mmi_levels))
  for (i in seq_along(mmi_levels)) {
    lvl <- mmi_levels[i]
    binary_actual <- as.numeric(actual == lvl)
    roc_obj <- roc(binary_actual, prob_matrix[, lvl], quiet = TRUE)
    lines(1 - roc_obj$specificities, roc_obj$sensitivities, col = colors[i], lwd = 2)
    aucs[i] <- auc(roc_obj)
  }

  legend("bottomright",
         legend = paste0("MMI ", mmi_levels, " (AUC = ", round(aucs, 2), ")"),
         col = colors, lwd = 2, cex = 0.6)

  invisible(setNames(aucs, mmi_levels))
}
```

Imbalance preparation for all models(stage 1: class weight, stage 2: strata/sampsize for randomForest, stage 3: resampling train dataset).

```{r}
# Stage 1: 

class_freq <- table(train$reported_mmi)
class_wt   <- max(class_freq) / class_freq
class_freq
class_wt

# Stage 2: min samsize for Random Forest
min_class_size <- min(class_freq)
min_class_size

# Stage 3: resample - downsampling as no resource for upsampling

set.seed(1911)
train_balanced <- downSample(
  x = train[, c("Mw", "Repi_km", "Rhypo_km", "Rcentroid_km", "ln_Vs30", "fault_style")],
  y = train$reported_mmi, yname = "reported_mmi"
)

table(train_balanced$reported_mmi)
```

```{r}
tree_earthquake <- tree(reported_mmi ~., train)

summary(tree_earthquake)
```

```{r}
plot(tree_earthquake)
text(tree_earthquake, pretty = 0, cex = 0.8)
tree_earthquake
```

```{r}
cv_tree_earthquake <- cv.tree(tree_earthquake, FUN = prune.misclass, K = 10)

plot(cv_tree_earthquake$size, cv_tree_earthquake$dev, type = 'b')
```

Cross validation shows 2 to 4 node is acceptable. Prune and check.

```{r}
prune_eq_2 <- prune.misclass(tree_earthquake, best = 2)

plot(prune_eq_2)
text(prune_eq_2, pretty = 0, cex = 0.8)
```

```{r}
prune_eq_3 <- prune.misclass(tree_earthquake, best = 3)

plot(prune_eq_3)
text(prune_eq_3, pretty = 0, cex = 0.8)
```

```{r}
prune_eq_4 <- prune.misclass(tree_earthquake, best = 4)

plot(prune_eq_4)
text(prune_eq_4, pretty = 0, cex = 0.8)
```

Checking trees with confusing matrix

```{r}
prune_2_pred <- predict(prune_eq_2, test, type = 'class')

table(prune_2_pred, test$reported_mmi)
```

```{r}
prune_3_pred <- predict(prune_eq_3, test, type = 'class')

table(prune_3_pred, test$reported_mmi)
```

```{r}
prune_4_pred <- predict(prune_eq_4, test, type = 'class')

table(prune_4_pred, test$reported_mmi)
```

Three prune tree share the same confusing matrix. 

ROC tree baseline

```{r}
prune3_prob <- predict(prune_eq_3, test, type = "vector")

eval_tree_base <- eval_summary(prune_3_pred, prune3_prob, test$reported_mmi, "Tree (prune, best=3) - baseline")
```

```{r}
plot_ovr_roc(prune3_prob, test$reported_mmi, "Tree (prune, best=3) - baseline")
```

Imbalance treatment Tree

Stage 1 and 2 is not supported, applying Stage 3 `train_balanced`.

```{r}
set.seed(1911)

tree_balanced <- tree(reported_mmi ~., data = train_balanced)

cv_tree_balanced <- cv.tree(tree_balanced, FUN = prune.misclass, K = 10)
best_size_bal <- max(cv_tree_balanced$size[which.min(cv_tree_balanced$dev)], 2)

prune_tree_balanced <- prune.misclass(tree_balanced, best = best_size_bal)
```

```{r}
pred_tree_bal <- predict(prune_tree_balanced, test, type = "class")
prob_tree_bal <- predict(prune_tree_balanced, test, type = "vector")

eval_tree_bal <- eval_summary(pred_tree_bal, prob_tree_bal, test$reported_mmi, "Tree - Tier 3 (downsampled train)")
```

```{r}
plot_ovr_roc(prob_tree_bal, test$reported_mmi, "Tree - Tier 3 (downsampled train)")
```

Not very high, as high as wild guess

Build tree using library Rpart

```{r}
set.seed(1911)

tree_rpart <- rpart(reported_mmi ~., data = train, method = "class", control = rpart.control(cp = 0, minsplit = 2)
)

tree_rpart$cptable
#plotcp(tree_rpart)
#plot(tree_rpart)
#text(tree_rpart, pretty = 0, cex = 0.8)
```

```{r}
min(tree_rpart$cptable[, "xerror"])

min_cv <- which.min(tree_rpart$cptable[, "xerror"]) 
prune_rpart <- prune(tree_rpart, cp = tree_rpart$cptable[min_cv, "CP"])
```

```{r}
plot(prune_rpart, main = "prune tree")
text(prune_rpart, cex = 0.6)
```

```{r}
pred_rpart <- predict(prune_rpart, test, type = "class")

rpart_matrix <- table( Predicted = pred_rpart,Actual = test$reported_mmi)


```



ROC / AUC Rpart (baseline)

```{r}
rpart_prob <- predict(prune_rpart, test, type = "prob")

eval_rpart_base <- eval_summary(pred_rpart, rpart_prob, test$reported_mmi, "Rpart - baseline")
```

```{r}
plot_ovr_roc(rpart_prob, test$reported_mmi, "Rpart - baseline")
```

Imbalance treatment Rpart

Stage 1: 'parms = list(prior = ...)' to set all classes equal when choosing branch."w" means weight

```{r}
set.seed(1911)

tree_rpart_w <- rpart(reported_mmi ~., data = train, method = "class", control = rpart.control(cp = 0, minsplit = 2), parms = list(prior = rep(1 / n_class, n_class)))

min_cv_w <- which.min(tree_rpart_w$cptable[, "xerror"])
prune_rpart_w <- prune(tree_rpart_w, cp = tree_rpart_w$cptable[min_cv_w, "CP"])
```

```{r}
pred_rpart_w <- predict(prune_rpart_w, test, type = "class")
prob_rpart_w <- predict(prune_rpart_w, test, type = "prob")

eval_rpart_w <- eval_summary(pred_rpart_w, prob_rpart_w, test$reported_mmi, "Rpart - Tier 1 (class weight/prior)")
```

```{r}
plot_ovr_roc(prob_rpart_w, test$reported_mmi, "Rpart - Tier 1 (class weight/prior)")
```

Stage 2 rpart don't support
Stage 3:

```{r}
set.seed(1911)

tree_rpart_bal <- rpart(reported_mmi ~., data = train_balanced, method = "class", control = rpart.control(cp = 0, minsplit = 2))

min_cv_bal <- which.min(tree_rpart_bal$cptable[, "xerror"])
prune_rpart_bal <- prune(tree_rpart_bal, cp = tree_rpart_bal$cptable[min_cv_bal, "CP"])
```

```{r}
pred_rpart_bal <- predict(prune_rpart_bal, test, type = "class")
prob_rpart_bal <- predict(prune_rpart_bal, test, type = "prob")

eval_rpart_bal <- eval_summary(pred_rpart_bal, prob_rpart_bal, test$reported_mmi, "Rpart - Tier 3 (downsampled train)")
```

```{r}
plot_ovr_roc(prob_rpart_bal, test$reported_mmi, "Rpart - Tier 3 (downsampled train)")
```

Bagging

```{r}
set.seed(1911)

bagging <- randomForest(reported_mmi ~., data = train, mtry = 6, ntree = 1000, importance = TRUE, do.trace = 100)

bagging
```

```{r}
bag_pred <- predict(bagging, test)

bag_matrix <- table(Predicted = bag_pred, Actual = test$reported_mmi)

bag_matrix
```


```{r}
importance(bagging, type = 2)
varImpPlot(bagging, type = 2)
```

ROC / AUC  Bagging (baseline)

```{r}
bag_prob <- predict(bagging, test, type = "prob")

eval_bag_base <- eval_summary(bag_pred, bag_prob, test$reported_mmi, "Bagging - baseline")
```

```{r}
plot_ovr_roc(bag_prob, test$reported_mmi, "Bagging - baseline")
```

Imbalance treatment Bagging

Stage 1: 'classwt'

```{r}
set.seed(1911)

bagging_w <- randomForest(reported_mmi ~., data = train, mtry = 6, ntree = 1000, importance = TRUE, classwt = class_wt, do.trace = 100)
```

```{r}
bag_pred_w <- predict(bagging_w, test)
bag_prob_w <- predict(bagging_w, test, type = "prob")

eval_bag_w <- eval_summary(bag_pred_w, bag_prob_w, test$reported_mmi, "Bagging - Tier 1 (class weight)")
```

```{r}
plot_ovr_roc(bag_prob_w, test$reported_mmi, "Bagging - Tier 1 (class weight)")
```

Stage 2: strata/sampsize 

```{r}
set.seed(1911)

bagging_strata <- randomForest(reported_mmi ~., data = train, mtry = 6, ntree = 1000, importance = TRUE, strata = train$reported_mmi, sampsize = rep(min_class_size, n_class), do.trace = 100)
```

```{r}
bag_pred_strata <- predict(bagging_strata, test)
bag_prob_strata <- predict(bagging_strata, test, type = "prob")

eval_bag_strata <- eval_summary(bag_pred_strata, bag_prob_strata, test$reported_mmi, "Bagging - Tier 2 (strata/sampsize)")
```

```{r}
plot_ovr_roc(bag_prob_strata, test$reported_mmi, "Bagging - Tier 2 (strata/sampsize)")
```

Stage 3: resampling `train_balanced`.

```{r}
set.seed(1911)

bagging_bal <- randomForest(reported_mmi ~., data = train_balanced, mtry = 6, ntree = 1000, importance = TRUE, do.trace = 100)
```

```{r}
bag_pred_bal <- predict(bagging_bal, test)
bag_prob_bal <- predict(bagging_bal, test, type = "prob")

eval_bag_bal <- eval_summary(bag_pred_bal, bag_prob_bal, test$reported_mmi, "Bagging - Tier 3 (downsampled train)")
```

```{r}
plot_ovr_roc(bag_prob_bal, test$reported_mmi, "Bagging - Tier 3 (downsampled train)")
```

Random forest

```{r}
set.seed(1911)

rf <- randomForest(reported_mmi ~., data = train, ntree = 1000, importance = TRUE, do.trace = 100)

rf
```

```{r}
importance(rf, type = 2)
varImpPlot(rf, type = 2, main = "Variable Importance - Random Forest")
```


Bagging and random forest have a bit higher accuracy and recall of MMi but still not desirable.

ROC / AUC Random Forest (baseline)

```{r}
rf_prob <- predict(rf, test, type = "prob")

eval_rf_base <- eval_summary(rf_pred, rf_prob, test$reported_mmi, "Random Forest - baseline")
```

```{r}
plot_ovr_roc(rf_prob, test$reported_mmi, "Random Forest - baseline")
```

Imbalance treatment Random Forest

Stage 1: `classwt`.

```{r}
set.seed(1911)

rf_w <- randomForest(reported_mmi ~., data = train, ntree = 1000, importance = TRUE, classwt = class_wt, do.trace = 100)
```

```{r}
rf_pred_w <- predict(rf_w, test)
rf_prob_w <- predict(rf_w, test, type = "prob")

eval_rf_w <- eval_summary(rf_pred_w, rf_prob_w, test$reported_mmi, "Random Forest - Tier 1 (class weight)")
```

```{r}
plot_ovr_roc(rf_prob_w, test$reported_mmi, "Random Forest - Tier 1 (class weight)")
```

Stage 2: strata/sampsize

```{r}
set.seed(1911)

rf_strata <- randomForest(reported_mmi ~., data = train, ntree = 1000, importance = TRUE, strata = train$reported_mmi, sampsize = rep(min_class_size, n_class), do.trace = 100)
```

```{r}
rf_pred_strata <- predict(rf_strata, test)
rf_prob_strata <- predict(rf_strata, test, type = "prob")

eval_rf_strata <- eval_summary(rf_pred_strata, rf_prob_strata, test$reported_mmi, "Random Forest - Tier 2 (strata/sampsize)")
```

```{r}
plot_ovr_roc(rf_prob_strata, test$reported_mmi, "Random Forest - Tier 2 (strata/sampsize)")
```

Stage 3: resampling `train_balanced`.

```{r}
set.seed(1911)

rf_bal <- randomForest(rreported_mmi ~., data = train_balanced, ntree = 1000, importance = TRUE, do.trace = 100)
```

```{r}
rf_pred_bal <- predict(rf_bal, test)
rf_prob_bal <- predict(rf_bal, test, type = "prob")

eval_rf_bal <- eval_summary(rf_pred_bal, rf_prob_bal, test$reported_mmi, "Random Forest - Tier 3 (downsampled train)")
```

```{r}
plot_ovr_roc(rf_prob_bal, test$reported_mmi, "Random Forest - Tier 3 (downsampled train)")
```

Boosting

```{r}
set.seed(1911)

boost <- gbm(reported_mmi ~., data = train, distribution = "multinomial", n.trees = 1000, interaction.depth = 4, shrinkage = 0.01, n.minobsinnode = 10, cv.folds = 5, verbose = FALSE)

summary(boost)
```

Boost tree is different from decision tree, random forest, it pays more attention to Mw and distance variable than Vs30.

```{r}
optimize_boost <- gbm.perf(boost, method = "OOB")
optimize_boost
```

```{r}
boost_prob <- predict(boost, test, n.trees = optimize_boost, type = "response")
boost_prob <- drop(boost_prob)

boost_pred <- colnames(boost_prob)[max.col(boost_prob)]

boost_pred <- factor(boost_pred,levels = levels(test$reported_mmi))

boost_matrix <- table(Predicted = boost_pred, Actual = test$reported_mmi)

boost_matrix
```


ROC / AUC  Boosting (baseline)

```{r}
eval_boost_base <- eval_summary(boost_pred, boost_prob, test$reported_mmi, "Boosting - baseline")
```

```{r}
plot_ovr_roc(boost_prob, test$reported_mmi, "Boosting - baseline")
```

Imbalance treatment Boosting

Stage 1: weight

```{r}
set.seed(1911)

obs_wt <- 1 / class_freq[as.character(train$reported_mmi)]

boost_w <- gbm(reported_mmi ~., data = train, distribution = "multinomial", n.trees = 1000, interaction.depth = 4, shrinkage = 0.01, n.minobsinnode = 10, cv.folds = 5, weights = obs_wt, verbose = FALSE)

optimize_boost_w <- gbm.perf(boost_w, method = "OOB")
```

```{r}
boost_prob_w <- predict(boost_w, test, n.trees = optimize_boost_w, type = "response")
boost_prob_w <- drop(boost_prob_w)

boost_pred_w <- colnames(boost_prob_w)[max.col(boost_prob_w)]
boost_pred_w <- factor(boost_pred_w, levels = levels(test$reported_mmi))

eval_boost_w <- eval_summary(boost_pred_w, boost_prob_w, test$reported_mmi, "Boosting - Tier 1 (observation weights)")
```

```{r}
plot_ovr_roc(boost_prob_w, test$reported_mmi, "Boosting - Tier 1 (observation weights)")
```

Stage 2 dont support go to Stage 3.

```{r}
set.seed(1911)

boost_bal <- gbm(reported_mmi ~., data = train_balanced, distribution = "multinomial", n.trees = 1000, interaction.depth = 4, shrinkage = 0.01, n.minobsinnode = 10, cv.folds = 5, verbose = FALSE)

optimize_boost_bal <- gbm.perf(boost_bal, method = "OOB")
```

```{r}
boost_prob_bal <- predict(boost_bal, test, n.trees = optimize_boost_bal, type = "response")
boost_prob_bal <- drop(boost_prob_bal)

boost_pred_bal <- colnames(boost_prob_bal)[max.col(boost_prob_bal)]
boost_pred_bal <- factor(boost_pred_bal, levels = levels(test$reported_mmi))

eval_boost_bal <- eval_summary(boost_pred_bal, boost_prob_bal, test$reported_mmi, "Boosting - Tier 3 (downsampled train)")
```

```{r}
plot_ovr_roc(boost_prob_bal, test$reported_mmi, "Boosting - Tier 3 (downsampled train)")
```

Combining table of result

```{r}
summary_table <- data.frame(
  Model = c(
    "Tree - baseline", "Tree - Tier 3",
    "Rpart - baseline", "Rpart - Tier 1", "Rpart - Tier 3",
    "Bagging - baseline", "Bagging - Tier 1", "Bagging - Tier 2", "Bagging - Tier 3",
    "Random Forest - baseline", "Random Forest - Tier 1", "Random Forest - Tier 2", "Random Forest - Tier 3",
    "Boosting - baseline", "Boosting - Tier 1", "Boosting - Tier 3"
  ),
  Accuracy = c(
    eval_tree_base$accuracy, eval_tree_bal$accuracy,
    eval_rpart_base$accuracy, eval_rpart_w$accuracy, eval_rpart_bal$accuracy,
    eval_bag_base$accuracy, eval_bag_w$accuracy, eval_bag_strata$accuracy, eval_bag_bal$accuracy,
    eval_rf_base$accuracy, eval_rf_w$accuracy, eval_rf_strata$accuracy, eval_rf_bal$accuracy,
    eval_boost_base$accuracy, eval_boost_w$accuracy, eval_boost_bal$accuracy
  ),
  Balanced_Accuracy = c(
    eval_tree_base$balanced_accuracy, eval_tree_bal$balanced_accuracy,
    eval_rpart_base$balanced_accuracy, eval_rpart_w$balanced_accuracy, eval_rpart_bal$balanced_accuracy,
    eval_bag_base$balanced_accuracy, eval_bag_w$balanced_accuracy, eval_bag_strata$balanced_accuracy, eval_bag_bal$balanced_accuracy,
    eval_rf_base$balanced_accuracy, eval_rf_w$balanced_accuracy, eval_rf_strata$balanced_accuracy, eval_rf_bal$balanced_accuracy,
    eval_boost_base$balanced_accuracy, eval_boost_w$balanced_accuracy, eval_boost_bal$balanced_accuracy
  ),
    Macro_Precision = c(
      mean(eval_tree_base$precision, na.rm = TRUE), mean(eval_tree_bal$precision, na.rm = TRUE),
      mean(eval_rpart_base$precision, na.rm = TRUE), mean(eval_rpart_w$precision, na.rm = TRUE), mean(eval_rpart_bal$precision, na.rm = TRUE),
      mean(eval_bag_base$precision, na.rm = TRUE), mean(eval_bag_w$precision, na.rm = TRUE), mean(eval_bag_strata$precision, na.rm = TRUE), mean(eval_bag_bal$precision, na.rm = TRUE),
      mean(eval_rf_base$precision, na.rm = TRUE), mean(eval_rf_w$precision, na.rm = TRUE), mean(eval_rf_strata$precision, na.rm = TRUE), mean(eval_rf_bal$precision, na.rm = TRUE),
      mean(eval_boost_base$precision, na.rm = TRUE), mean(eval_boost_w$precision, na.rm = TRUE), mean(eval_boost_bal$precision, na.rm = TRUE)
  ),
  AUC = c(
    eval_tree_base$auc, eval_tree_bal$auc,
    eval_rpart_base$auc, eval_rpart_w$auc, eval_rpart_bal$auc,
    eval_bag_base$auc, eval_bag_w$auc, eval_bag_strata$auc, eval_bag_bal$auc,
    eval_rf_base$auc, eval_rf_w$auc, eval_rf_strata$auc, eval_rf_bal$auc,
    eval_boost_base$auc, eval_boost_w$auc, eval_boost_bal$auc
  )
)

summary_table[order(-summary_table$Balanced_Accuracy), ]
```

