---
title: "R Notebook"
output: html_notebook
---

1. Split earthquakes into train/test
2. calculate best_lambda using only train_data
3. create the Box–Cox response
4. fit models
5. predict test data
6. inverse Box–Cox predictions
7. calculate RMSE in MMI units.

# Data Preparation
loads the final processed Felt RAPID dataset, which includes the earthquake data, Felt RAPID observations, and Vs30 site-condition data produced in `05_add_vs30_site_conditions.R`.
The dataset is then filtered to require a minimum of four Felt RAPID reports per spatial cell, reducing the influence of cells where the reported MMI is based on only a small number of individual reports.

```{r}
library(arrow)
library(MASS)
library(tidyverse)
library(sf)
library(leaps)
library(lme4)
library(here)
library(viridis)
library(dplyr)

data <- read_parquet(
  here("data_processed", "NZ_FR_IAR_final_dataset.parquet")
)


```

```{r}
# Expected columns in the modelling dataset
expected_columns <- c(
  "publicid",
  "cell_id",
  "origintime",
  "event_longitude",
  "event_latitude",
  "event_depth_km",
  "report_longitude",
  "report_latitude",
  "reported_mmi",
  "report_count",
  "Mw",
  "Repi_km",
  "Rhypo_km",
  "Vs30_m_s"
)

# Check all expected columns are present
stopifnot(
  all(expected_columns %in% names(data))
)


# Check earthquake-cell combinations are unique
stopifnot(
  nrow(data) ==
    nrow(distinct(data, publicid, cell_id))
)


# Check important values are usable
stopifnot(
  all(data$report_count >= 0, na.rm = TRUE),
  all(data$Rhypo_km >= 0, na.rm = TRUE),
  all(data$Repi_km >= 0, na.rm = TRUE),
  all(data$event_depth_km >= 0, na.rm = TRUE),
  all(data$reported_mmi > 0, na.rm = TRUE)
)


# Confirm existing earthquake selection rules
stopifnot(
  all(data$origintime >= as.POSIXct("2016-09-01", tz = "UTC")),
  all(data$Mw > 3.5, na.rm = TRUE)
)


# Check earthquake-level attributes are consistent within publicid
event_check <- data |>
  group_by(publicid) |>
  summarise(
    n_origintime = n_distinct(origintime),
    n_event_longitude = n_distinct(event_longitude),
    n_event_latitude = n_distinct(event_latitude),
    n_event_depth = n_distinct(event_depth_km),
    n_Mw = n_distinct(Mw),
    .groups = "drop"
  )

stopifnot(
  all(event_check$n_origintime == 1),
  all(event_check$n_event_longitude == 1),
  all(event_check$n_event_latitude == 1),
  all(event_check$n_event_depth == 1),
  all(event_check$n_Mw == 1)
)
```

```{r}
# Minimum total Felt RAPID reports required per cell and then per earthquake
data_sd <- data |>
  filter(report_count >= 4) |>
  group_by(publicid) |>
  mutate(
    total_reports = sum(report_count, na.rm = TRUE)
  ) |>
  filter(total_reports >= 4) |>
  ungroup()
```

```{r}
set.seed(123)

# Get unique earthquakes
earthquake_ids <- unique(data_sd$publicid)

# Randomly select 80% of earthquakes for training
train_ids <- sample(
  earthquake_ids,
  size = floor(0.8 * length(earthquake_ids))
)

# Split data by earthquake
train_data <- data_sd |>
  filter(publicid %in% train_ids)

test_data <- data_sd |>
  filter(!publicid %in% train_ids)
```

```{r}
model_bc <- regsubsets(
  reported_mmi ~ event_depth_km + Repi_km + Rhypo_km + Vs30_m_s + Mw,
  data = train_data,
  nvmax = 4
)

summary(model_bc)
plot(model_bc)
summary(model_bc)$bic
```

```{r}
# Function for applying the Box-Cox transformation
boxcox_transform <- function(y, lambda, tol = 1e-8) {
  
  if (any(y <= 0, na.rm = TRUE)) {
    stop("Box-Cox transformation requires positive response values.")
  }
  
  if (abs(lambda) < tol) {
    log(y)
  } else {
    (y^lambda - 1) / lambda
  }
}
```

```{r}
bc_1 <- boxcox(
  lm(reported_mmi ~ Mw + Rhypo_km,
  data = train_data)
)

best_lambda_1 <- bc_1$x[which.max(bc_1$y)]
cat("Best lambda:", best_lambda_1, "\n")

# Transform reported MMI using the selected lambda
train_data <- train_data |>
  mutate(
    reported_mmi_bc_1 = boxcox_transform(
      reported_mmi,
      best_lambda_1
    )
  )

# Fit model using the transformed response
model_lr1 <- lm(
  reported_mmi_bc_1 ~ Mw + Rhypo_km,
  data = train_data
)

plot(model_lr1)
summary(model_lr1)
```

```{r}
bc_2 <- boxcox(
  lm(reported_mmi ~ event_depth_km + Mw + Repi_km,
  data = train_data)
)

best_lambda_2 <- bc_2$x[which.max(bc_2$y)]
cat("Best lambda:", best_lambda_2, "\n")

# Transform reported MMI using the selected lambda
train_data <- train_data |>
  mutate(
    reported_mmi_bc_2 = boxcox_transform(
      reported_mmi,
      best_lambda_2
    )
  )

# Fit model using the transformed response
model_lr2 <- lm(
  reported_mmi_bc_2 ~ event_depth_km + Mw + Repi_km,
  data = train_data
)

plot(model_lr2)
summary(model_lr2)
```

```{r}
bc_3 <- boxcox(
  lm(reported_mmi ~ event_depth_km + Mw + Repi_km + Vs30_m_s,
  data = train_data)
)

best_lambda_3 <- bc_3$x[which.max(bc_3$y)]
cat("Best lambda:", best_lambda_3, "\n")

# Transform reported MMI using the selected lambda
train_data <- train_data |>
  mutate(
    reported_mmi_bc_3 = boxcox_transform(
      reported_mmi,
      best_lambda_3
    )
  )

# Fit model using the transformed response
model_lr3 <- lm(
  reported_mmi_bc_3 ~ event_depth_km + Mw + Repi_km + Vs30_m_s,
  data = train_data
)

plot(model_lr3)
summary(model_lr3)
```

```{r}
# Check that log transformations are valid
stopifnot(
  all(train_data$Repi_km > 0, na.rm = TRUE),
  all(train_data$Vs30_m_s > 0, na.rm = TRUE)
)

# Original predictor forms
model_lr_1 <- lm(
  reported_mmi_bc_3 ~ event_depth_km + Mw + Repi_km + Vs30_m_s,
  data = train_data
)

# Log distance
model_lr_2 <- lm(
  reported_mmi_bc_3 ~ event_depth_km + Mw + log10(Repi_km) + Vs30_m_s,
  data = train_data
)

# Log Vs30
model_lr_3 <- lm(
  reported_mmi_bc_3 ~ event_depth_km + Mw + Repi_km + log10(Vs30_m_s),
  data = train_data
)

# Log distance and log Vs30
model_lr_4 <- lm(
  reported_mmi_bc_3 ~ event_depth_km + Mw + log10(Repi_km) + log10(Vs30_m_s),
  data = train_data
)

# Linear + log distance
model_lr_5 <- lm(
  reported_mmi_bc_3 ~ event_depth_km + Mw + Repi_km + log10(Repi_km) + (Vs30_m_s),
  data = train_data
)

# Linear + log distance and log Vs30
model_lr_6 <- lm(
  reported_mmi_bc_3 ~ event_depth_km + Mw + Repi_km + log10(Repi_km) + log10(Vs30_m_s),
  data = train_data
)

AIC(
  model_lr_1,
  model_lr_2,
  model_lr_3,
  model_lr_4,
  model_lr_5,
  model_lr_6
)

```

```{r}
# Fit candidate mixed models

# Model 1: linear distance and linear Vs30
model_mixed_1 <- lmer(
  reported_mmi ~ event_depth_km + Mw + Repi_km + Vs30_m_s + (1 + Repi_km | publicid),
  data = train_data,
  REML = FALSE
)


# Model 2: log distance and linear Vs30
model_mixed_2 <- lmer(
  reported_mmi ~ event_depth_km + Mw + log10(Repi_km) + Vs30_m_s + (1 + log10(Repi_km) | publicid),
  data = train_data,
  REML = FALSE
)


# Model 3: linear + log distance and log Vs30
model_mixed_3 <- lmer(
  reported_mmi ~ event_depth_km + Mw + Repi_km + log10(Repi_km) + log(Vs30_m_s) + (1 + log10(Repi_km) | publicid),
  data = train_data,
  REML = FALSE
)

# 3. Predict unseen earthquakes
pred_1 <- predict(
    model_mixed_1,
    newdata = train_data,
    re.form = NA,
    allow.new.levels = TRUE
)

pred_2 <- predict(
    model_mixed_2,
    newdata = train_data,
    re.form = NA,
    allow.new.levels = TRUE
)

pred_3 <- predict(
    model_mixed_3,
    newdata = train_data,
    re.form = NA,
    allow.new.levels = TRUE
)

# 4. Calculate RMSE on original MMI scale
rmse_1 <- sqrt(
  mean((train_data$reported_mmi - pred_1)^2, na.rm = TRUE)
)

rmse_2 <- sqrt(
  mean((train_data$reported_mmi - pred_2)^2, na.rm = TRUE)
)

rmse_3 <- sqrt(
  mean((train_data$reported_mmi - pred_3)^2, na.rm = TRUE)
)

# 5. Compare results
rmse_results <- tibble(
  Model = c(
    "Linear Repi + linear Vs30",
    "Log10 Repi + linear Vs30",
    "Linear + log10 Repi + log Vs30"
  ),
  RMSE = c(
    rmse_1,
    rmse_2,
    rmse_3
  )
) |>
  arrange(RMSE)

rmse_results
```

```{r}
# Compare response transformations
# Predictor structure is kept the same

# Model 4: No response transformation
model_mixed_4 <- lmer(
  reported_mmi ~ event_depth_km + Mw + log10(Repi_km) + Vs30_m_s + (1 + log10(Repi_km) | publicid),
  data = train_data,
  REML = FALSE
)


# Model 5: Log response transformation
model_mixed_5 <- lmer(
  log(reported_mmi) ~ event_depth_km + Mw + log10(Repi_km) + Vs30_m_s + (1 + log10(Repi_km) | publicid),
  data = train_data,
  REML = FALSE
)


# Model 6: Box-Cox response transformation
model_mixed_6 <- lmer(
  reported_mmi_bc_3 ~ event_depth_km + Mw + log10(Repi_km) + Vs30_m_s + (1 + log10(Repi_km) | publicid),
  data = train_data,
  REML = FALSE
)

# Predict training data for model comparison

# Raw MMI: already on original MMI scale
pred_4 <- predict(
  model_mixed_4,
  newdata = train_data,
  re.form = NA,
  allow.new.levels = TRUE
)


# Log MMI: convert back using exp()
pred_5 <- exp(
  predict(
    model_mixed_5,
    newdata = train_data,
    re.form = NA,
    allow.new.levels = TRUE
  )
)


# Box-Cox: first get predictions on Box-Cox scale
pred_6_bc <- predict(
  model_mixed_6,
  newdata = train_data,
  re.form = NA,
  allow.new.levels = TRUE
)


# Inverse Box-Cox function
inverse_boxcox <- function(z, lambda, tol = 1e-8) {
  
  if (abs(lambda) < tol) {
    return(exp(z))
  }
  
  inside <- 1 + lambda * z
  
  result <- rep(NA_real_, length(z))
  valid <- inside > 0
  
  result[valid] <- inside[valid]^(1 / lambda)
  
  if (any(!valid)) {
    warning("Some Box-Cox predictions could not be back-transformed.")
  }
  
  return(result)
}


# Convert Box-Cox predictions back to original MMI scale
pred_6 <- inverse_boxcox(
  pred_6_bc,
  best_lambda_3
)

# Calculate RMSE on original MMI scale
rmse_4 <- sqrt(
  mean((train_data$reported_mmi - pred_4)^2, na.rm = TRUE)
)

rmse_5 <- sqrt(
  mean((train_data$reported_mmi - pred_5)^2, na.rm = TRUE)
)

rmse_6 <- sqrt(
  mean((train_data$reported_mmi - pred_6)^2, na.rm = TRUE)
)

# Compare results
rmse_results <- tibble(
  Model = c(
    "Raw MMI",
    "Log MMI",
    paste0("Box-Cox MMI (lambda = ", round(best_lambda_3, 3), ")")
  ),
  RMSE = c(
    rmse_4,
    rmse_5,
    rmse_6
  )
) |>
  arrange(RMSE)

rmse_results
```

```{r}
# Linear model prediction on Box-Cox scale
pred_lm_bc <- predict(
  model_lr_6,
  newdata = test_data
)

# Convert back to original MMI scale
pred_lm <- inverse_boxcox(
  pred_lm_bc,
  best_lambda_3
)

# Mixed-effects model prediction
# model_mixed_4 predicts raw MMI already
pred_mixed <- predict(
  model_mixed_4,
  newdata = test_data,
  re.form = NA,
  allow.new.levels = TRUE
)

# Calculate RMSE on original MMI scale
rmse_lm <- sqrt(
  mean(
    (test_data$reported_mmi - pred_lm)^2,
    na.rm = TRUE
  )
)

rmse_mixed <- sqrt(
  mean(
    (test_data$reported_mmi - pred_mixed)^2,
    na.rm = TRUE
  )
)

# Final comparison
tibble(
  Model = c(
    "Linear model",
    "Mixed-effects model"
  ),
  RMSE = c(
    rmse_lm,
    rmse_mixed
  )
) |>
  arrange(RMSE)
```

```{r}
data_sd |>
  filter(!is.na(reported_mmi)) |>
  count(publicid, name = "reported_mmi_count") |>
  arrange(desc(reported_mmi_count)) |>
  slice_head(n = 10)

```

```{r}
high_mmi_earthquakes <- data_sd |>
  filter(reported_mmi %in% c(6, 7, 8)) |>
  group_by(publicid) |>
  summarise(
    mmi_6 = sum(reported_mmi == 6),
    mmi_7 = sum(reported_mmi == 7),
    mmi_8 = sum(reported_mmi == 8),
    total_6_7_8 = sum(reported_mmi %in% c(6, 7, 8)),
    Mw = first(Mw),
    event_depth_km = first(event_depth_km),
    .groups = "drop"
  ) |>
  arrange(desc(total_6_7_8))

high_mmi_earthquakes
```

```{r}
unzip("statsnz-regional-council-2025-clipped-GPKG.zip", exdir = "nzmap")
nzmap <- st_read("nzmap/regional-council-2025-clipped.gpkg")
```

```{r}
# Choose earthquake
earthquake_id <- "2023p122368"

# Get data for selected earthquake
eq_data <- data_sd |>
  filter(publicid == earthquake_id)

# Predicted MMI at actual Felt RAPID locations
eq_pred_bc <- predict(
  model_lr_6,
  newdata = eq_data
)

eq_data$predicted_mmi <- inverse_boxcox(
  eq_pred_bc,
  best_lambda_3
)

# Convert Felt RAPID locations to spatial points
eq_sf <- eq_data |>
  st_as_sf(
    coords = c(
      "report_longitude",
      "report_latitude"
    ),
    crs = 4326,
    remove = FALSE
  ) |>
  st_transform(2193)

# Get earthquake epicentre
earthquake <- eq_data |>
  slice(1) |>
  st_as_sf(
    coords = c(
      "event_longitude",
      "event_latitude"
    ),
    crs = 4326
  ) |>
  st_transform(2193)


# Convert NZ map to NZTM
nz_nztm <- nzmap |>
  st_transform(2193)

# Values for this earthquake
mw_value <- eq_data$Mw[1]

depth <- eq_data$event_depth_km[1]

# Hold Vs30 constant so predicted regions can be circular
vs30_value <- median(
  eq_data$Vs30_m_s,
  na.rm = TRUE
)

# Generate predictions over epicentral distance
prediction_data <- tibble(
  Repi_km = seq(
    from = 0.1,
    to = max(data_sd$Repi_km, na.rm = TRUE),
    by = 0.1
  ),
  event_depth_km = depth,
  Mw = mw_value,
  Vs30_m_s = vs30_value
)


# Predict on Box-Cox scale
prediction_bc <- predict(
  model_lr_6,
  newdata = prediction_data
)

# Convert predictions back to MMI scale
prediction_data$predicted_mmi <- inverse_boxcox(
  prediction_bc,
  best_lambda_3
)

# Get prediction range
minimum_predicted <- min(
  prediction_data$predicted_mmi,
  na.rm = TRUE
)

maximum_predicted <- max(
  prediction_data$predicted_mmi,
  na.rm = TRUE
)

print(
  c(
    minimum_predicted = minimum_predicted,
    maximum_predicted = maximum_predicted
  )
)

# Define MMI category boundaries
mmi_boundaries <- seq(
  2.5,
  7.5,
  by = 1
)

mmi_boundaries <- mmi_boundaries[
  mmi_boundaries >= minimum_predicted &
    mmi_boundaries <= maximum_predicted
]

# Find epicentral distance where each boundary occurs
ring_distances <- map_dfr(
  mmi_boundaries,
  function(boundary) {

    closest <- prediction_data |>
      slice_min(
        abs(predicted_mmi - boundary),
        n = 1,
        with_ties = FALSE
      )

    tibble(
      boundary = boundary,
      Repi_km = closest$Repi_km,
      predicted_mmi = closest$predicted_mmi
    )
  }
)

print(ring_distances)

# Give each circle its integer MMI value
rings <- ring_distances |>
  mutate(
    radius_km = Repi_km,
    mmi = ceiling(boundary)
  ) |>
  arrange(desc(radius_km))

# Create circle geometry
ring_geometry <- lapply(
  rings$radius_km,
  function(radius) {

    st_buffer(
      st_geometry(earthquake),
      dist = radius * 1000
    )[[1]]

  }
)

rings_sf <- st_sf(
  boundary = rings$boundary,
  radius_km = rings$radius_km,
  mmi = rings$mmi,
  geometry = st_sfc(
    ring_geometry,
    crs = 2193
  )
)

# Create labels
epicentre_coords <- st_coordinates(
  earthquake
)[1, ]

circle_labels <- rings_sf |>
  st_drop_geometry() |>
  filter(mmi != 6) |>
  mutate(
    x = epicentre_coords[1] + radius_km * 1000,
    y = epicentre_coords[2],
    label = paste("MMI", mmi)
  ) |>
  st_as_sf(
    coords = c("x", "y"),
    crs = 2193
  )

# Create map
mmi_map <- ggplot() +

  geom_sf(
    data = nz_nztm,
    fill = "grey95",
    colour = "grey60"
  ) +

  # Predicted MMI regions
  geom_sf(
    data = rings_sf,
    aes(fill = mmi),
    colour = "black",
    linewidth = 0.4,
    alpha = 0.65
  ) +

  # MMI labels
  geom_sf_label(
    data = circle_labels,
    aes(label = label),
    size = 3.5,
    fontface = "bold",
    fill = "white",
    nudge_x = -100000
  ) +

  # Observed MMI
  geom_sf(
    data = eq_sf,
    aes(colour = reported_mmi),
    size = 1,
    alpha = 0.7
  ) +

  # Earthquake epicentre
  geom_sf(
    data = earthquake,
    shape = 4,
    size = 4,
    stroke = 1.5
  ) +

  scale_colour_viridis_c(
    limits = c(3, 8),
    breaks = 3:8,
    name = "MMI"
  ) +

  scale_fill_viridis_c(
    limits = c(3, 8),
    breaks = 3:8,
    name = "MMI"
  ) +

  labs(
    title = "Observed and Predicted Earthquake Intensity",
    subtitle = paste(
      "Earthquake:",
      earthquake_id
    ),
    x = NULL,
    y = NULL
  ) +

  theme_void() +

  theme(
    legend.position = "right",
    plot.title = element_text(
      face = "bold"
    )
  )


# Display map
mmi_map
```

```{r}
# Create earthquake_maps folder inside Project-Silvanus
dir.create(
  here("earthquake_maps"),
  showWarnings = FALSE
)

# Save map
ggsave(
  filename = here(
    "earthquake_maps",
    paste0("MMI_map_", earthquake_id, ".png")
  ),
  plot = mmi_map,
  width = 10,
  height = 8,
  units = "in",
  dpi = 300
)
```

```{r}
# HYPOTHETICAL EARTHQUAKE MMI MAP

# Define hypothetical earthquake
earthquake_name <- "Hypothetical Earthquake"

# Change these values for the earthquake you want to model
event_longitude <- 172.6
event_latitude  <- -43.5
mw_value        <- 6.0
depth           <- 15
vs30_value      <- 400

# Create earthquake epicentre
earthquake <- tibble(
  longitude = event_longitude,
  latitude = event_latitude
) |>
  st_as_sf(
    coords = c(
      "longitude",
      "latitude"
    ),
    crs = 4326
  ) |>
  st_transform(2193)

# Convert NZ map to NZTM
nz_nztm <- nzmap |>
  st_transform(2193)

# Generate hypocentral distances
prediction_data <- tibble(
  Rhypo_km = seq(
    from = depth,
    to = 10000,
    by = 0.1
  ),
  Mw = mw_value,
  Vs30_m_s = vs30_value
)

# Predict MMI
# re.form = NA means:
# use fixed effects only because this is a new earthquake
# with no known earthquake-specific random effect
prediction_data$predicted_mmi <- exp(
  predict(
    model_mem_5,
    newdata = prediction_data,
    re.form = NA
  )
)

# Get prediction range
minimum_predicted <- min(
  prediction_data$predicted_mmi,
  na.rm = TRUE
)

maximum_predicted <- max(
  prediction_data$predicted_mmi,
  na.rm = TRUE
)


print(
  c(
    minimum_predicted = minimum_predicted,
    maximum_predicted = maximum_predicted
  )
)

# Define boundaries between integer MMI categories
# Starting at 2.5 means no MMI 2 circle is drawn.
mmi_boundaries <- seq(
  2.5,
  7.5,
  by = 1
)


# Only keep boundaries actually crossed by model
mmi_boundaries <- mmi_boundaries[
  mmi_boundaries >= minimum_predicted &
    mmi_boundaries <= maximum_predicted
]

# Find hypocentral distance of each MMI boundary
ring_distances <- purrr::map_dfr(
  mmi_boundaries,
  function(boundary) {

    closest <- prediction_data |>
      slice_min(
        abs(predicted_mmi - boundary),
        n = 1,
        with_ties = FALSE
      )

    tibble(
      boundary = boundary,
      Rhypo_km = closest$Rhypo_km,
      predicted_mmi = closest$predicted_mmi
    )
  }
)

# Convert hypocentral distance to horizontal map distance
#
# Rhypo^2 = Repi^2 + depth^2
# therefore:
# Repi = sqrt(Rhypo^2 - depth^2)
ring_distances <- ring_distances |>
  mutate(
    radius_km = sqrt(
      pmax(
        Rhypo_km^2 - depth^2,
        0
      )
    )
  )


print(ring_distances)

# Give each predicted region its integer MMI
rings <- ring_distances |>
  mutate(
    mmi = ceiling(boundary)
  ) |>
  arrange(desc(radius_km))

# Create circular MMI regions
ring_geometry <- lapply(
  rings$radius_km,
  function(radius) {

    st_buffer(
      st_geometry(earthquake),
      dist = radius * 1000
    )[[1]]

  }
)


rings_sf <- st_sf(
  boundary = rings$boundary,
  radius_km = rings$radius_km,
  mmi = rings$mmi,
  geometry = st_sfc(
    ring_geometry,
    crs = 2193
  )
)

# Get epicentre coordinates
epicentre_coords <- st_coordinates(
  earthquake
)[1, ]

# Create labels on right-hand side of circles
#
# MMI 6 is excluded from the labels.
# Remove "filter(mmi != 6)" if you want it back.
circle_labels <- rings_sf |>
  st_drop_geometry() |>
  filter(mmi != 6) |>
  mutate(

    # Right-hand edge of each circle
    x = epicentre_coords[1] +
      radius_km * 1000,

    y = epicentre_coords[2],

    label = paste(
      "MMI",
      mmi
    )
  ) |>
  st_as_sf(
    coords = c("x", "y"),
    crs = 2193
  )

# Create map
mmi_map <- ggplot() +

  # NZ map
  geom_sf(
    data = nz_nztm,
    fill = "grey95",
    colour = "grey60"
  ) +

  # Predicted MMI regions
  geom_sf(
    data = rings_sf,
    aes(fill = mmi),
    colour = "black",
    linewidth = 0.4,
    alpha = 0.65
  ) +

  # MMI labels
  geom_sf_label(
    data = circle_labels,
    aes(label = label),
    size = 3.5,
    fontface = "bold",
    fill = "white",
    nudge_x = -10000
  ) +

  # Earthquake epicentre
  geom_sf(
    data = earthquake,
    shape = 4,
    size = 4,
    stroke = 1.5
  ) +

  # MMI colour scale
  scale_fill_viridis_c(
    limits = c(3, 8),
    breaks = 3:8,
    name = "MMI"
  ) +

  # Titles
  labs(
    title = "Predicted Earthquake Intensity",
    subtitle = paste0(
      earthquake_name,
      " | Mw ",
      mw_value,
      " | Depth ",
      depth,
      " km"
    ),
    x = NULL,
    y = NULL
  ) +

  # Remove coordinate grid and axis labels
  theme_void() +

  theme(
    legend.position = "right",
    plot.title = element_text(
      face = "bold"
    )
  )

# Display map
mmi_map


# Create earthquake_maps folder if it does not exist
dir.create(
  here::here("earthquake_maps"),
  showWarnings = FALSE
)
```

```{r}
# Save map
ggsave(
  filename = here::here(
    "earthquake_maps",
    paste0(
      "MMI_map_hypothetical_Mw",
      mw_value,
      "_depth",
      depth,
      "km.png"
    )
  ),
  plot = mmi_map,
  width = 10,
  height = 8,
  units = "in",
  dpi = 300
)
```







