---
title: "R Notebook"
output: html_notebook
---

# Data Preparation
Reads the two datasets and joins the Vs30 data to the main dataset based on the nearest Vs30 data point.

```{r}
library(arrow)
library(MASS)
library(tidyverse)
library(sf)
library(leaps)
library(lme4)
library(here)
library(viridis)

data <- read_parquet(
  here("data_processed", "NZ_FR_IAR_final_dataset.parquet")
)


data <- data |>
  drop_na(
    Rhypo_km,
    Mw,
    Vs30_raw,
    event_depth_km,
    publicid
  )


# filters the dataset to the decided upon report count
data_sd <- data |>
  filter(report_count >= 4)
```

# Box-Cox Model

Trying out other predictors and applying best subset selection.

```{r}
model_bc <- regsubsets(
  reported_mmi ~ event_depth_km + Rhypo_km + Vs30_raw + Mw + geonet_catalogue_magnitude,
  data = data_sd,
  nvmax = 4
)

summary(model_bc)
plot(model_bc)
summary(model_bc)$bic
```


# Checking Vs30 data as no model wants to use it

Uses a Box-Cox transformation to find the most suitable transformation of `felt_mmi_median_cells` for only Vs30.

```{r}
bc <- boxcox(
  lm(reported_mmi ~ Mw + Rhypo_km + geonet_catalogue_magnitude + Vs30_raw, data = data_sd)
)

best_lambda <- bc$x[which.max(bc$y)]
best_lambda
```
```{r}
model_lr <- lm(
  ((reported_mmi^-0.3434343 - 1) / -0.3434343) ~ Mw + Rhypo_km + geonet_catalogue_magnitude + Vs30_raw,
  data = data_sd
  )

plot(model_lr)
summary(model_lr)
```


# Best Subset Selection

Uses best subset selection to compare combinations of earthquake depth, hypocentral distance, moment magnitude and Vs30 for predicting the Median MMI.


```{r}
model_lr_rss <- regsubsets(
  reported_mmi ~ event_depth_km + Rhypo_km + Vs30_raw + Mw,
  data = data_sd,
  nvmax = 4
)

summary(model_lr_rss)
plot(model_lr_rss)
summary(model_lr_rss)$bic
```

# Filtering Felt Reports

With the selected variables applies a Box-Cox analysis to determine the most suitable transformation for the filtered data.

```{r}
model_lr_bc <- boxcox(
  lm(reported_mmi ~ event_depth_km + Rhypo_km + Vs30_raw + Mw, data = data_sd)
)

best_lambda <- model_lr_bc$x[which.max(model_lr_bc$y)]
best_lambda
```



# Selected Linear Model — Full Dataset

Fits the model selected from the best subset analysis and boxcox transformations and checks its model summary and diagnostic plots.

```{r}
model_lr <- lm(
  ((reported_mmi^-0.3434343 - 1) / -0.3434343) ~ event_depth_km + Rhypo_km + Vs30_raw + Mw,
  data = data_sd
  )

plot(model_lr)
summary(model_lr)
```

# Mixed-Effects Model

Fits a linear mixed-effects model with earthquake ID (`publicid`) as a random effect to account for multiple observations coming from the same earthquake.
still very Work in progress

```{r}
model_mem_1 <- lmer(
  log(reported_mmi) ~ Rhypo_km + (1 | publicid), data = data_sd,
  REML = FALSE
  )
summary(model_mem_1)
cat("\n")

model_mem_2 <- lmer(
  log(reported_mmi) ~ Rhypo_km + Mw + (1 | publicid), data = data_sd,
  REML = FALSE
  )
summary(model_mem_2)
cat("\n")

model_mem_3 <- lmer(
  log(reported_mmi) ~ Rhypo_km + Mw + Vs30_raw + (1 | publicid), data = data_sd,
  REML = FALSE
  )
summary(model_mem_3)
cat("\n")

model_mem_4 <- lmer(
  log(reported_mmi) ~ Rhypo_km + Mw + Vs30_raw + event_depth_km + (1 | publicid), data = data_sd,
  REML = FALSE
  )
summary(model_mem_4)
cat("\n")


anova(model_mem_1, model_mem_2, model_mem_3, model_mem_4)
```

```{r}
data_sd |>
  filter(!is.na(reported_mmi)) |>
  count(publicid, name = "reported_mmi_count") |>
  arrange(desc(reported_mmi_count)) |>
  slice_head(n = 5)

```

```{r}
unzip("statsnz-regional-council-2025-clipped-GPKG.zip", exdir = "nzmap")
nzmap <- st_read("nzmap/regional-council-2025-clipped.gpkg")
```

```{r}
# Choose earthquake
earthquake_id <- "2021p169083"


# Get data for selected earthquake
eq_data <- data_sd |>
  filter(publicid == earthquake_id)

# Predicted MMI at actual Felt RAPID locations
#
# re.form = NULL includes the random effect for this earthquake

eq_data$predicted_mmi <- exp(
  predict(
    model_mem_3,
    newdata = eq_data,
    re.form = NULL
  )
)

# Convert Felt RAPID locations to spatial points

eq_sf <- eq_data |>
  st_as_sf(
    coords = c(
      "report_longitude",
      "report_latitude"
    ),
    crs = 4326,
    remove = FALSE
  ) |>
  st_transform(2193)

# Get earthquake epicentre
earthquake <- eq_data |>
  slice(1) |>
  st_as_sf(
    coords = c(
      "event_longitude",
      "event_latitude"
    ),
    crs = 4326
  ) |>
  st_transform(2193)

# Convert NZ map to NZTM
nz_nztm <- nzmap |>
  st_transform(2193)


# Values for this earthquake
mw_value <- eq_data$Mw[1]

depth <- eq_data$event_depth_km[1]

# Hold Vs30 constant so predicted regions can be circular
vs30_value <- median(
  eq_data$Vs30_raw,
  na.rm = TRUE
)

# Generate predicted MMI over hypocentral distance
#
# Start at earthquake depth because when epicentral distance
# is zero:
#
# Rhypo = depth
#
# Predict out to 1000 km so lower MMI boundaries can be found.
prediction_data <- tibble(
  Rhypo_km = seq(
    from = depth,
    to = 10000,
    by = 0.1
  ),
  Mw = mw_value,
  Vs30_raw = vs30_value,
  publicid = earthquake_id
)

prediction_data$predicted_mmi <- exp(
  predict(
    model_mem_3,
    newdata = prediction_data,
    re.form = NULL
  )
)

# Check prediction range
minimum_predicted <- min(
  prediction_data$predicted_mmi,
  na.rm = TRUE
)

maximum_predicted <- max(
  prediction_data$predicted_mmi,
  na.rm = TRUE
)

print(
  c(
    minimum_predicted = minimum_predicted,
    maximum_predicted = maximum_predicted
  )
)

# Define boundaries between integer MMI categories
#
# For example:
#
# 3.5 separates MMI 3 and MMI 4
# 4.5 separates MMI 4 and MMI 5
# 5.5 separates MMI 5 and MMI 6
mmi_boundaries <- seq(
  1.5,
  7.5,
  by = 1
)


# Only keep boundaries that the model actually crosses
mmi_boundaries <- mmi_boundaries[
  mmi_boundaries >= minimum_predicted &
  mmi_boundaries <= maximum_predicted
]

# Find hypocentral distance where each boundary occurs
ring_distances <- map_dfr(
  mmi_boundaries,
  function(boundary) {

    closest <- prediction_data |>
      slice_min(
        abs(predicted_mmi - boundary),
        n = 1,
        with_ties = FALSE
      )

    tibble(
      boundary = boundary,
      Rhypo_km = closest$Rhypo_km,
      predicted_mmi = closest$predicted_mmi
    )
  }
)

# Convert hypocentral distance to horizontal map distance
#
# Rhypo^2 = Repi^2 + depth^2
#
# Therefore:
#
# Repi = sqrt(Rhypo^2 - depth^2)
ring_distances <- ring_distances |>
  mutate(
    radius_km = sqrt(
      pmax(
        Rhypo_km^2 - depth^2,
        0
      )
    )
  )

# Check boundary distances
print(ring_distances)

# Create spatial circles
ring_geometry <- lapply(
  ring_distances$radius_km,
  function(radius) {

    st_buffer(
      st_geometry(earthquake),
      dist = radius * 1000
    )[[1]]

  }
)


rings <- st_sf(
  boundary = ring_distances$boundary,
  radius_km = ring_distances$radius_km,
  geometry = st_sfc(
    ring_geometry,
    crs = 2193
  )
)

# Create labels for predicted MMI regions

# Get earthquake coordinates
epicentre_coords <- st_coordinates(earthquake)[1, ]

# Order boundaries from smallest radius to largest
label_data <- ring_distances |>
  arrange(radius_km)

# Create inner and outer radius of each region
region_edges <- c(
  0,
  label_data$radius_km,
  max(label_data$radius_km) + 100
)

# MMI at the centre of each region
centre_mmi <- round(maximum_predicted)

region_labels <- tibble(
  mmi = centre_mmi - seq_along(head(region_edges, -1)) + 1,
  radius_km = (
    head(region_edges, -1) +
    tail(region_edges, -1)
  ) / 2
)

# Put labels to the east of the epicentre
region_labels_sf <- st_as_sf(
  region_labels |>
    mutate(
      x = epicentre_coords[1] + radius_km * 1000,
      y = epicentre_coords[2],
      label = paste("MMI", mmi)
    ),
  coords = c("x", "y"),
  crs = 2193
)

mmi_map <- ggplot() +

  geom_sf(
    data = nz_nztm,
    fill = "grey95",
    colour = "grey60"
  ) +

  # Predicted MMI boundaries
  geom_sf(
    data = rings,
    fill = NA,
    linewidth = 1
  ) +

  # Observed reported MMI - smaller points
  geom_sf(
    data = eq_sf,
    aes(colour = reported_mmi),
    size = 1,
    alpha = 0.7
  ) +

  # Predicted MMI region labels
  geom_sf_label(
    data = region_labels_sf,
    aes(label = label),
    size = 4,
    fontface = "bold",
    fill = "white"
  ) +

  # Earthquake epicentre
  geom_sf(
    data = earthquake,
    shape = 4,
    size = 4,
    stroke = 1.5
  ) +

  scale_colour_viridis_c(
    limits = c(3, 8),
    breaks = 1:8,
    name = "Reported MMI"
  ) +

  labs(
    title = "Observed and Predicted Earthquake Intensity",
    subtitle = paste("Earthquake:", earthquake_id),
    x = NULL,
    y = NULL
  ) +

  theme_minimal()

# Display map
mmi_map
```

```{r}
ggsave(
  filename = paste0(
    "MMI_map_",
    earthquake_id,
    ".png"
  ),
  plot = mmi_map,
  width = 10,
  height = 8,
  units = "in",
  dpi = 300
)
```

```{r}
test <- read_parquet(
  here("data_processed", "NZ_FR_IAR_dataset_all.parquet")
)
```




